### 2020-05-01 final_report/data.tex
final edits

Confirming our expectation that in the latter, trivial case the
autoencoder should achieve greater dimensional reduction, we are inclined to
believe that our implementation is indeed operating as intended. However, we
must also conclude that in both examined cases this method failed to produce a
reduction that would prove superior to a naïve approach.\footnote{In both tested cases we
	can trivially eliminate 6~dimensions due to overdetermination of one-hot-encoded
	categorical features, and 2~dimensions corresponding to sum-to-one constraints. Furthermore, in the
	single slice case we may omit 6~additional dimensions due to fixed feature
	assignment.} This is consistent with previous results obtained by PCA and kriging.

>>>>

Confirming our expectation that in the latter, trivial case the
autoencoder should achieve greater dimensional reduction, we are inclined to
believe that our implementation is indeed operating as intended. However, we
must also conclude that in both examined cases this method failed to produce a
reduction that would prove superior to a naïve approach.\footnote{In both tested cases we
	can trivially eliminate 6~dimensions due to overdetermination of one-hot-encoded
	categorical features, and 2~dimensions corresponding to sum-to-one constraints. Furthermore, in the
	single slice case we may omit 6~additional dimensions due to fixed feature
	assignment.} This is consistent with the previous results obtained by PCA and kriging.
